---
title: "IKUNML Workflow"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{IKUNML Workflow}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

## Overview

IKUNML wraps several feature-selection methods for omics-style classification
data and exports method-specific results, plots, overlap summaries, reports,
stability selection results, and validation outputs.

## Example Data

```{r}
library(IKUNML)

data <- read.csv(
  system.file("extdata", "example_data.csv", package = "IKUNML"),
  row.names = 1,
  check.names = FALSE
)
```

## Run Feature Selection

```{r}
res <- run_feature_selection(
  data,
  group_col = "group",
  methods = c("lasso", "SVM", "rf"),
  output_dir = "IKUNML_results",
  method_params = list(
    lasso = list(alpha = 0.5, lambda_choice = "lambda.min"),
    SVM = list(k = 10, halve_above = 50, max_features = 200, tolerance = 0.02),
    rf = list(ntree = 1000, cv_ntree = 300, max_features = 200, tolerance = 0.02)
  )
)
```

## Review Overlaps

```{r}
feature_intersection(res)
feature_hit_summary(res)
write_ikun_report(res, output_dir = "IKUNML_results")
```

## Stability Selection

```{r}
stab <- stability_selection(
  data,
  group_col = "group",
  methods = c("lasso", "SVM", "rf"),
  n_iter = 100,
  sample_fraction = 0.8,
  min_frequency = 0.6,
  parallel = TRUE,
  cores = 8,
  output_dir = "IKUNML_stability"
)
```

## Validate Selected Features

```{r}
val <- validate_selected_features(
  data,
  result = res,
  min_hits = 2,
  group_col = "group",
  positive_class = "Tumor",
  model = "glm",
  output_dir = "IKUNML_validation"
)
```

## Nested Cross-Validation

```{r}
ncv <- nested_cv_feature_selection(
  data,
  group_col = "group",
  methods = c("lasso", "SVM", "rf"),
  min_hits = 2,
  model = "glm",
  outer_folds = 5,
  output_dir = "IKUNML_nested_cv"
)
```

## Quiet Startup

IKUNML prints a random startup message by default. Disable it for scripts:

```{r}
options(IKUNML.startup = FALSE)
library(IKUNML)
```
